Paper summary

### 2022-07-25 paper/summary.tex
fixed some tests

\begin{equation}
  \label{eq:ALE_expectation}
  \mu(x_S) = \mathbb{E}_{\mathbf{x_c}|x_s}\left [\frac{\partial
      f}{\partial x_s} \right ]
\end{equation}

@@

\begin{equation}
  \label{eq:2}
  \sigma^2(x_S) = \mathrm{Var}_{\mathbf{x_c}|x_s}\left [\frac{\partial
      f}{\partial x_s} \right ]
\end{equation}

@@

>>>>

\begin{equation}
  \label{eq:ALE_mean}
  \mu(x_S) = \mathbb{E}_{\mathbf{x_c}|x_s}\left [\frac{\partial
      f}{\partial x_s} \right ]
\end{equation}

@@

\begin{equation}
  \label{eq:ALE_var}
  \sigma^2(x_S) = \mathrm{Var}_{\mathbf{x_c}|x_s}\left [\frac{\partial
      f}{\partial x_s} \right ]
\end{equation}

@@

\section{Toy Example}

\paragraph{Example 1.} We use the following example:

\begin{equation}
  \label{eq:model_1}
  \begin{gathered}
    f(x_1, x_2) = b_0 + b_1 x_1 + b_2 x_2 + b_3 x_1 x_2\\
    x_1 \sim \mathcal{U}(0,1) \\
    x_2 = x_1 + \epsilon, \epsilon \sim \mathcal{N}(\mu=0, \sigma_2^2)
  \end{gathered}
\end{equation}
%
Therefore, according to Eq.~(\ref{eq:ALE_mean})
\(\mu_(x_1) = b_1 + b_3 x_1\) and according to Eq.~(\ref{eq:ALE_var})
\(\sigma^2(x_1) = b_3^2 \sigma_2^2 \Rightarrow \sigma(x_1) = b_3
\sigma_2 \).

\paragraph{ALE with uncertainty.}

In figure~\ref{fig:bullet-1-im-3} we observe the ALE effect with
uncertainty for 3 different values of \(\sigma_2 = \{0.01, 0.1,
1\}\). In all case the mean effect (ALE) is the same, but the
uncertainty of the global explanation quantifies the impact of the
heterogeneous effects hiding behing the global explanation.

\begin{figure}[!h]
  \centering
  \includegraphics[width=.32\linewidth]{./example_gromping_paper/ALE_gt_s2_0_01.png}
  \includegraphics[width=.32\linewidth]{./example_gromping_paper/ALE_gt_s2_0_1.png}
  \includegraphics[width=.32\linewidth]{./example_gromping_paper/ALE_gt_s2_1_0.png}
  \caption{ALE (a) \(\sigma_2^2 = 0.01\), (b) \(\sigma_2^2 = 0.1\), (c) \(\sigma_2^2 = 1.\)}
  \label{fig:bullet-1-im-3}
\end{figure}

\paragraph{Bin Splitting.}

In figure~\ref{fig:im2}, set up for
\(b_0=0, b_1=1, b_2=1, b_3=2, \sigma_2^2 = 0.1\). Therefore, the
unavoidable uncertainty is \(\sigma^2(x_1) = b_3^2 \sigma_2^2 =
0.4\). We observe that as the bins become more dense the added
uncertainty due to binning becomes less. But as the bins become more
dense, less points lie inside them and the estimation is poor. The
vertical lines show the maximum number of bins for dataset sizes, if I
want at least 25 points per bin.

\begin{figure}[!h]
  \centering
  \includegraphics[width=.7\linewidth]{./example_gromping_paper/bin_varinace.png}
  \caption{}
  \label{fig:im2}
\end{figure}
